---
title: "Analysis"
author: Resid(COVID) + Joe Choo, Glen Morgenstern, Carrie Wang, and Zhixue (Mary) Wang
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Research Question

The coronavirus has hit perhaps no American city quite as hard as New York, where more than 10,000 residents have died due to it. Yet, New Yorkers have heard conflicting advice from Governer Andrew Cuomo and President Donald Trump. Our team decided to look at how the stay-at-home order and other advice from government officials affected how New Yorkers drive. With reduced traffic, are accidents down? Has the lockdown affected New York's six boroughs differently?

Motivating question: **How has government guidance affected New York drivers' motivations and safety?**

## Data

The data comes from the City of New York's website. This data set consists of police reports on all motor vehicle collisions in New York City  as of April 18. A police report is warranted when there is a fatality or injury or damage of $1000 or more. Our analysis will focus only on collisions in 2020.

You can find the updated data set at: https://data.cityofnewyork.us/Public-Safety/Motor-Vehicle-Collisions-Crashes/h9gi-nx95?fbclid=IwAR1UoErhqzmJrviRZ4zkpYu7cHhOgCAA417o6A3rhrIZSKrXPPNVjdzsWUQ

## Set Up

```{r}
library(tidyverse)
library(lubridate)
```

```{r cars}
data <- read.csv("data/Motor_Vehicle_Collisions_-_Crashes.csv")
```

Dates to look at:
Jan 20 - First reported US case
Feb 9 - Death toll in China surpasses SARS epidemic (811 deaths)
Feb 29 - First death on American soil
March 1 - First confirmed case in NYC
March 7 - Cuomo declares state of emergency
March 11 - WHO declares pandemic, Trump bans travel from 26 European countries
March 13 - Trump declares national emergency
March 14 - First coronavirus death in NYC
March 16 - NYC schools close (ordered by Cuomo)
March 17 - De Blasio says NYC considering order, Cuomo says it won't happen; schools, bar, restaurants close in NYC (de Blasio)
March 20 - Cuomo orders lockdown
March 22 - Lockdown starts (8pm)
March 28 - Trump signs $2.2 trillion stimulus bill
April 3 - CDC recommends wearing masks
April 6 - Cuomo extends stay at home order to April 29
April 14 - Cuomo says he would defy Trump order to reopen New York
April 16 - Cuomo extends stay at home order to May 15
April 17 - Trump tweets "Liberate" Minnesota, Michigan, Virginia

## Data Wrangling

Make all street names upper case.
```{r}
data$ON.STREET.NAME = toupper(data$ON.STREET.NAME)
data$OFF.STREET.NAME = toupper(data$OFF.STREET.NAME)
data$CROSS.STREET.NAME = toupper(data$CROSS.STREET.NAME)
```

Confirm no duplicate collision IDs.
```{r}
data[duplicated(data$COLLISION_ID), ]
```
No duplicates---all good.

```{r}
data <- data %>%
  select(-X)
```

```{r}
data %>%
   count(CONTRIBUTING.FACTOR.VEHICLE.1)
```

Regroup so that accerlator defective, brakes defective, windshield inadequate, tire failure, tow hitch defective, headlights defective, and other lighting defects are in one group called mechanical defect; using on board navigation device, texting, cell phone (hand-held), cell phone (hands-free), and other electronic device are under distraction; listening is under distracted; fatigued/drowsy, fell asleep, and lost consciousness are under drowsy; pavement defective, shoulders defective, and pavement slippery under environment.

```{r}
data <- data %>%
  mutate(CONTRIBUTING.FACTOR.VEHICLE.1 = as.character(CONTRIBUTING.FACTOR.VEHICLE.1)) %>%
   mutate(CONTRIBUTING.FACTOR.VEHICLE.1 = case_when(
     CONTRIBUTING.FACTOR.VEHICLE.1 == ""  ~ "Unspecified",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Glare"  ~ "View Obstructed/Limited",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Tire Failure/Inadequate"  ~ "Mechanical Defect",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Windshield Inadequate"  ~ "Mechanical Defect",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Tow Hitch Defective"  ~ "Mechanical Defect",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Accelerator Defective"  ~ "Mechanical Defect",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Brakes Defective"  ~ "Mechanical Defect",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Headlights Defective"  ~ "Mechanical Defect",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Other Lighting Defects"  ~ "Mechanical Defect",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Cell Phone (hand-Held)"  ~ "Driver Inattention/Distraction",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Listening/Using Headphones"  ~ "Driver Inattention/Distraction",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Other Electronic Device"  ~ "Driver Inattention/Distraction",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Using On Board Navigation Device"  ~ "Driver Inattention/Distraction",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Cell Phone (hands-free)"  ~ "Driver Inattention/Distraction",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Outside Car Distraction"  ~ "Driver Inattention/Distraction",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Passenger Distraction"  ~ "Driver Inattention/Distraction",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Texting"  ~ "Driver Inattention/Distraction",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Eating or Drinking"  ~ "Driver Inattention/Distraction",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Fatigued/Drowsy"  ~ "Tired",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Fell Asleep"  ~ "Tired",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Lost Consciousness"  ~ "Tired",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Lane Marking Improper/Inadequate"  ~ "Road Environment",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Obstruction/Debris"  ~ "Road Environment",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Pavement Defective"  ~ "Road Environment",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Pavement Slippery"  ~ "Road Environment",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Shoulders Defective/Improper"  ~ "Road Environment",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Prescription Medication"  ~ "Health",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Physical Disability"  ~ "Health",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Illnes"  ~ "Health",
     CONTRIBUTING.FACTOR.VEHICLE.1 == "Traffic Control Device Improper/Non-Working"  ~ "Road Environment",
    CONTRIBUTING.FACTOR.VEHICLE.1 == "Tinted Windows"  ~ "View Obstructed/Limited",
     TRUE ~ CONTRIBUTING.FACTOR.VEHICLE.1
   ))
```

```{r}
data %>%
   count(CONTRIBUTING.FACTOR.VEHICLE.1)
```

```{r}
data %>%
   count(VEHICLE.TYPE.CODE.1)
```

Regroup so EMERG, AMB, AMBU, AMBUL, amb, ambul are under ambulance; BOX T is under Box Truck; DELIV, DELV, deliv, devli, Deliv are under delivery; DUMP, dump is under dump; FIRE, Fire, Firet, fire, and FIRET and under Firetruck; FLATB is under Flat Bed; FORK and FORKL is under Forlift; PICKU, pick, and Pickup with mounted is under Pick-up Truck; SCHOO, schoo, Schoo under School Bus; all wheeler sednas under Sedan; Tow, tow truck, tow t, under tow truck; UTIL, UTILI, Utili under utility

```{r}
data <- data %>%
  mutate(VEHICLE.TYPE.CODE.1 = as.character(VEHICLE.TYPE.CODE.1)) %>%
   mutate(VEHICLE.TYPE.CODE.1 = case_when(
     VEHICLE.TYPE.CODE.1 == "van" ~ "Van",
     VEHICLE.TYPE.CODE.1 == "UTIL" ~ "Utility",
     VEHICLE.TYPE.CODE.1 == "UTILI" ~ "Utility",
     VEHICLE.TYPE.CODE.1 == "Utili" ~ "Utility",
     VEHICLE.TYPE.CODE.1 == "" ~ "Unknown",
     VEHICLE.TYPE.CODE.1 == "TOW T" ~ "Tow Truck",
     VEHICLE.TYPE.CODE.1 == "Tow" ~ "Tow Truck",
     VEHICLE.TYPE.CODE.1 == "Tow t" ~ "Tow Truck",
     VEHICLE.TYPE.CODE.1 == "Tow Truck / Wrecker" ~ "Tow Truck",
     VEHICLE.TYPE.CODE.1 == "TRK" ~ "Truck",
     VEHICLE.TYPE.CODE.1 == "TRUCK" ~ "Truck",
     VEHICLE.TYPE.CODE.1 == "2 dr sedan" ~ "Sedan",
     VEHICLE.TYPE.CODE.1 == "3-Door" ~ "Sedan",
     VEHICLE.TYPE.CODE.1 == "4 dr sedan" ~ "Sedan",
     VEHICLE.TYPE.CODE.1 == "REFG" ~ "Refrigerated Van",
     VEHICLE.TYPE.CODE.1 == "pick" ~ "Pick-up Truck",
     VEHICLE.TYPE.CODE.1 == "PICKU" ~ "Pick-up Truck",
     VEHICLE.TYPE.CODE.1 == "Pickup with mounted Camper" ~ "Pick-up Truck",
     VEHICLE.TYPE.CODE.1 == "FORKL" ~ "Forklift",
     VEHICLE.TYPE.CODE.1 == "FORK" ~ "Forklift",
     VEHICLE.TYPE.CODE.1 == "FLATB" ~ "Flat Bed",
     VEHICLE.TYPE.CODE.1 == "TRAC" ~ "Tractor Truck",
     VEHICLE.TYPE.CODE.1 == "TRACT" ~ "Tractor Truck",
     VEHICLE.TYPE.CODE.1 == "Tract" ~ "Tractor Truck",
     VEHICLE.TYPE.CODE.1 == "tract" ~ "Tractor Truck",
     VEHICLE.TYPE.CODE.1 == "Tractor Truck Diesel" ~ "Tractor Truck",
     VEHICLE.TYPE.CODE.1 == "Tractor Truck Gasoline" ~ "Tractor Truck",
     VEHICLE.TYPE.CODE.1 == "SCHOO" ~ "School Bus",
     VEHICLE.TYPE.CODE.1 == "schoo" ~ "School Bus",
     VEHICLE.TYPE.CODE.1 == "Schoo" ~ "School Bus",
     VEHICLE.TYPE.CODE.1 == "Fire" ~ "Firetruck",
     VEHICLE.TYPE.CODE.1 == "Firet" ~ "Firetruck",
     VEHICLE.TYPE.CODE.1 == "FIRE" ~ "Firetruck",
     VEHICLE.TYPE.CODE.1 == "FIRET" ~ "Firetruck",
     VEHICLE.TYPE.CODE.1 == "fire" ~ "Firetruck",
     VEHICLE.TYPE.CODE.1 == "FIRE" ~ "Firetruck",
     VEHICLE.TYPE.CODE.1 == "EMERG" ~ "Ambulance",
     VEHICLE.TYPE.CODE.1 == "AMB" ~ "Ambulance",
     VEHICLE.TYPE.CODE.1 == "AMBU" ~ "Ambulance",
     VEHICLE.TYPE.CODE.1 == "AMBUL" ~ "Ambulance",
     VEHICLE.TYPE.CODE.1 == "ambul" ~ "Ambulance",
     VEHICLE.TYPE.CODE.1 == "Amb" ~ "Ambulance",
     VEHICLE.TYPE.CODE.1 == "Ambul" ~ "Ambulance",
     VEHICLE.TYPE.CODE.1 == "Ambulance" ~ "Ambulance",
     VEHICLE.TYPE.CODE.1 == "deliv" ~ "Delivery",
     VEHICLE.TYPE.CODE.1 == "delvi" ~ "Delivery",
     VEHICLE.TYPE.CODE.1 == "DELIV" ~ "Delivery",
     VEHICLE.TYPE.CODE.1 == "DELV" ~ "Delivery",
     VEHICLE.TYPE.CODE.1 == "Deliv" ~ "Delivery",
     VEHICLE.TYPE.CODE.1 == "DUMP" ~ "Dump",
     VEHICLE.TYPE.CODE.1 == "dump" ~ "Dump",
     VEHICLE.TYPE.CODE.1 == "BOX T" ~ "Box Truck",
     VEHICLE.TYPE.CODE.1 == "Bobca" ~ "Station Wagon/Sport Utility Vehicle",
     VEHICLE.TYPE.CODE.1 == "Armored Truck" ~ "Truck",
     VEHICLE.TYPE.CODE.1 == "Beverage Truck" ~ "Truck",
     VEHICLE.TYPE.CODE.1 == "truck" ~ "Truck",
     VEHICLE.TYPE.CODE.1 == "COM" ~ "Commercial",
     VEHICLE.TYPE.CODE.1 == "Comme" ~ "Commercial",
     VEHICLE.TYPE.CODE.1 == "FDNY" ~ "Firetruck",
     VEHICLE.TYPE.CODE.1 == "Fdny" ~ "Firetruck",
     VEHICLE.TYPE.CODE.1 == "ford" ~ "Ford",
     VEHICLE.TYPE.CODE.1 == "DIRT" ~ "Station Wagon/Sport Utility Vehicle",
     VEHICLE.TYPE.CODE.1 == "Unkno" ~ "Unknown",
     VEHICLE.TYPE.CODE.1 == "Van Camper" ~ "Van",
     VEHICLE.TYPE.CODE.1 == "moped" ~ "Moped",
     VEHICLE.TYPE.CODE.1 == "GOLF" ~ "Carry All",
     VEHICLE.TYPE.CODE.1 == "H1" ~ "Station Wagon/Sport Utility Vehicle",
     VEHICLE.TYPE.CODE.1 == "Hears" ~ "Hearse",
     VEHICLE.TYPE.CODE.1 == "Hopper" ~ "Freight",
     VEHICLE.TYPE.CODE.1 == "MTA" ~ "City",
     VEHICLE.TYPE.CODE.1 == "OMR" ~ "Omnibus",
     VEHICLE.TYPE.CODE.1 == "OMS" ~ "Omnibus",
     VEHICLE.TYPE.CODE.1 == "SCOOT" ~ "Motorscooter",
     VEHICLE.TYPE.CODE.1 == "TR-Tr" ~ "Trailer",
     VEHICLE.TYPE.CODE.1 == "TRAIL" ~ "Trailer",
     VEHICLE.TYPE.CODE.1 == "TRL" ~ "Trailer",
     VEHICLE.TYPE.CODE.1 == "Trail" ~ "Trailer",
     VEHICLE.TYPE.CODE.1 == "UNK" ~ "Unknown",
     VEHICLE.TYPE.CODE.1 == "US PO" ~ "USPS",
     VEHICLE.TYPE.CODE.1 == "posta" ~ "USPS",
     VEHICLE.TYPE.CODE.1 == "POSTA" ~ "USPS",
     VEHICLE.TYPE.CODE.1 == "MAIL" ~ "USPS",
     VEHICLE.TYPE.CODE.1 == "FREIG" ~ "Freight",
     TRUE ~ VEHICLE.TYPE.CODE.1
   ))
```

```{r}
data %>%
   count(VEHICLE.TYPE.CODE.1, sort = TRUE)
```

```{r}
data <- data %>%
   mutate(weekday = wday(mdy(CRASH.DATE), label = TRUE)) %>%
   separate(CRASH.DATE, c("month", "day", "year"), "/")
data <- data %>%
   mutate(day = as.numeric(day)) %>%
   mutate(month = as.numeric(month))
data <- data %>%
   mutate(daytot = case_when(
      month == "1" ~ day,
      month == "2" ~ day + 31,
      month == "3" ~ day + 60,
      TRUE ~ day + 91
   ))
data <- data %>%
  mutate(VEHICLE.TYPE.CODE.1new = fct_lump(VEHICLE.TYPE.CODE.1, n = 14, other_level = "Other"))
```

```{r stuff}
data %>%
   count(VEHICLE.TYPE.CODE.1new, sort = TRUE)
```

```{r}
data <- data %>%
   mutate(time_of_day = case_when(
      hm(CRASH.TIME) < hm("12:00") ~ "AM",
      TRUE ~ "PM"
   )) %>%
   mutate(person_tot = NUMBER.OF.PERSONS.INJURED + NUMBER.OF.PERSONS.KILLED)

```


### Exploratory Data Analysis
```{r eda}
data %>%
   ggplot(aes(x = weekday)) +
   geom_bar() +
   labs(x = "Day of Week",
        y = "Frequency")
data %>%
   count(weekday)
data %>%
   ggplot(aes(x = time_of_day)) +
   geom_bar() +
   labs(x = "Time of Day",
        y = "Frequency")
data %>%
   count(time_of_day)
data %>%
   ggplot(aes(x = person_tot)) +
   geom_histogram(breaks = seq(0, 10, by = 1)) +
   labs(x = "People Injured or Killed",
        y = "Frequency")
data %>%
   count(person_tot)
data %>%
   ggplot(aes(x = month)) +
   geom_bar() +
   labs(x = "Month",
        y = "Frequency")
### March lower, April not done yet but still proportionally even lower
data %>%
   ggplot(aes(x=daytot)) +
   geom_freqpoly()
data %>%
   ggplot(aes(x=daytot, y = count(daytot))) +
   geom_line()
data %>%
   count(month)
data %>%
  ggplot(aes(x = weekday, fill = time_of_day)) +
  geom_bar(position = "fill") +
  labs(title = "Relationship between Day of Week and Time of day",
       x = "Day of week", y = "Proportion")
###maybe more PM crashes on weekends?
data %>%
   ggplot(aes(x = weekday, y = person_tot)) +
   geom_boxplot() +
   labs(title = "Relationship between Day of Week and Killed/Injured",
       x = "day of week", y = "Killed/Injured")
data %>%
   ggplot(aes(x = as.character(month), y = person_tot)) +
   geom_boxplot() +
   labs(title = "Relationship between Month and Killed/Injured",
       x = "month", y = "Killed/Injured")
data %>%
  ggplot(aes(x = month, fill = VEHICLE.TYPE.CODE.1new)) +
  geom_bar(position = "fill") +
  labs(title = "Relationship between month and vehicle",
       x = "Month", y = "Proportion")
### maybe larger proportion of sedans compared to everything else now

```


```{r more stuff}
p <- ggmap(get_googlemap(center = c(lon = 40.7128, lat = 74.0060),
                    zoom = 11, scale = 2,
                    maptype ='terrain',
                    color = 'color'))
```
