---
title: "Analysis"
author: Resid(COVID) + Joe Choo, Glen Morgenstern, Carrie Wang, and Zhixue (Mary) Wang
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Research Question

The coronavirus has hit perhaps no American city quite as hard as New York, where more than 10,000 residents have died due to it. Yet, New Yorkers have heard conflicting advice from Governer Andrew Cuomo and President Donald Trump. Our team decided to look at how the stay-at-home order and other advice from government officials affected how New Yorkers drive. With reduced traffic, are accidents down? Has the lockdown affected New York's six boroughs differently?

Motivating question: **How has government guidance affected New York drivers' motivations and safety?**

## Data

The data comes from the City of New York's website. This data set consists of police reports on all motor vehicle collisions in New York City  as of April 18. A police report is warranted when there is a fatality or injury or damage of $1000 or more. Our analysis will focus only on collisions in 2020.

You can find the updated data set at: https://data.cityofnewyork.us/Public-Safety/Motor-Vehicle-Collisions-Crashes/h9gi-nx95?fbclid=IwAR1UoErhqzmJrviRZ4zkpYu7cHhOgCAA417o6A3rhrIZSKrXPPNVjdzsWUQ

## Set Up

```{r}
library(tidyverse)
```

```{r cars}
data <- read.csv("data/Motor_Vehicle_Collisions_-_Crashes.csv")
```

Dates to look at:
Jan 20 - First reported US case
Feb 9 - Death toll in China surpasses SARS epidemic (811 deaths)
Feb 29 - First death on American soil
March 1 - First confirmed case in NYC
March 11 - WHO declares pandemic, Trump bans travel from 26 European countries
March 13 - Trump declares national emergency
March 14 - First coronavirus death in NYC
March 17 - De Blasio says NYC considering order, Cuomo says it won't happen
March 20 - Cuomo orders lockdown
March 28 - Trump signs $2.2 trillion stimulus bill
April 3 - CDC recommends wearing masks
April 14 - Cuomo says he would defy Trump order to reopen New York
April 17 - Trump tweets "Liberate" Minnesota, Michigan, Virginia
 